Modern BTree techniques

### 2022-09-15 strangeloop/presentation.tex
Strangeloop

\usepackage[utf8]{inputenc}
\usepackage[russian, english]{babel}
\usepackage{booktabs}
\usepackage[scale=2]{ccicons}
\usepackage{listings}
\usepackage{marvosym}
\usepackage{color}
\usepackage{xcolor}
\usepackage[document]{ragged2e}
\usepackage[export]{adjustbox}
\usepackage{fontawesome}
\usepackage{enumitem}
\usepackage{minted}
\usemintedstyle{tango}
\usepackage[normalem]{ulem}
\usepackage{tikz}
\usetikzlibrary{patterns}
\usetikzlibrary{mindmap}
\usetikzlibrary{shapes.misc, fit}
\usepackage{graphicx}
\usepackage{eso-pic}
\usepackage{verbatim}
\usepackage{smartdiagram}
\usesmartdiagramlibrary{additions}
\usetikzlibrary{trees}
\usepackage{datetime}
\usepackage{hyperref}
\usepackage{forloop}
\usepackage{csquotes}
\usetikzlibrary{tikzmark}
\usetikzlibrary{arrows.meta}

@@

\usetikzlibrary{shapes,arrows,positioning}
\graphicspath{{images/}}
\newfontfamily{\FA}{FontAwesome}

\def\twitter{{\FA \faTwitter}}
\def\github{{\FA \faGithub}}
\def\email{{\FA \faEnvelope}}

\renewcommand{\ttdefault}{pcr}
\newfontfamily{\ttfamily}{Fira Code}

@@

\definecolor{links}{HTML}{0099FF}
\hypersetup{colorlinks, linkcolor=, urlcolor=links}
\definecolor{greenGood}{HTML}{99FF99}
\definecolor{redBad}{HTML}{FF9980}

@@

\pagenumbering{gobble}

\newdateformat{specialdate}{\twodigit{\THEDAY}-\twodigit{\THEMONTH}-\THEYEAR}

\def\strongdata{strong_correlation.data}
\def\weakdata{weak_correlation.data}

@@

  \vspace*{2.1cm}
  \begin{minipage}[b][\paperheight]{\textwidth}
  \begin{center}

    \ifx\inserttitle\@empty\else
    {{% \inserttitle is nonempty
      \raggedright%
      %\linespread{1.0}%
      \usebeamerfont{title}%
      \usebeamercolor[fg]{title}%
      %\vspace*{1.3em}
      \if@noSmallCapitals%
        \inserttitle%
      \else%
        \scshape{\color{black} \textbf{\begin{center}\inserttitle\end{center}}}%
      \fi%
      \vspace*{0.3em}
    }}
    \fi

@@

    \usebeamerfont{author}%
    \usebeamercolor[fg]{author}%
    {\color{black} \insertauthor}%

    \vspace*{1.5em}
    \fontsize{8pt}{10}\selectfont
    {\color{black} 31-01-2019}%

@@

\title{Modern BTree\\ techniques}
\subtitle{}
\date{\today}
\author{DMITRY DOLGOV}
\institute{}

@@

\begin{document}
{
  \usebackgroundtemplate{\includegraphics[width=\paperwidth]{template_2.png}}%
  \fontsize{17pt}{18}\selectfont
  \maketitle
}

\AddToShipoutPictureBG{
  \AtPagemyUpperLeft{{\includegraphics[width=2.0cm,keepaspectratio]{logo.png}}}
}%

\setbeamertemplate{background canvas}{
\begin{tikzpicture}
    \clip (0,0) rectangle (\paperwidth,\paperheight);
    \fill[color=orange] (4cm, \paperheight-6pt) rectangle (\paperwidth-4cm,\paperheight);
\end{tikzpicture}
}

@@

\begin{frame}
    \frametitle{}
    \begin{center}
        \only<1>{
            \includegraphics[width=0.5\textwidth,center]{tree.jpg}
            \vspace{-0.8cm}
            \hspace*{6cm}
            \href{https://www.flickr.com/photos/aspis7/5075169756/}
                 {\color{white}\fontsize{5pt}{0}\selectfont @aspis7}
        }
        \only<2>{
            \includegraphics[width=0.5\textwidth,center]{cs_tree.jpg}
            \vspace{-0.8cm}
            \hspace*{6cm}
            \href{https://www.flickr.com/photos/aspis7/5075169756/}
                 {\color{white}\fontsize{5pt}{0}\selectfont @aspis7}
        }
    \end{center}
\end{frame}

@@

    \only<3>
    {
        \begin{tikzpicture}[]
            \node [rum-extra-node] (complex) at ( 0, -3) {Complexity?};
            \node [rum-node] (memory) at ( 3, 0) {Mem};
            \node [rum-node] (write) at (-3, 0) {Write};
            \node [rum-node] (read) at ( 0, 3) {Read};
            \draw (read) -- (memory) -- (complex) -- (write) -- (read);
            \begin{scope}[on background layer]
                \fill [gray, opacity=0.2]
                    (read.center) --
                    (memory.center) --
                    (complex.center) --
                    (write.center) -- cycle;
            \end{scope}
        \end{tikzpicture}
    }

@@

        \onslide<2>
        \begin{tikzpicture}[]
            \node [rum-node] (memory) at ( 3, 0) {Mem};
            \node [rum-node] (write) at (-3, 0) {Write};
            \node [rum-node] (read) at ( 0, 3) {Read};
            \draw (read) -- (write) -- (memory) -- (read);
            \begin{scope}[on background layer]
                \fill [gray, opacity=0.2]
                    (read.center) --
                    (write.center) --
                    (memory.center) -- cycle;
            \end{scope}

            \coordinate[below=0.5 of read] (btree-pointer);
            \coordinate[right=2 of read] (btree-angle);
            \node[above=0.5 of btree-angle, draw=none] (btree) {B-Tree};
            \draw[->, line width=2pt] (btree)
                .. controls ([yshift=-2cm] btree) and (btree-pointer) ..
                (btree-pointer);
        \end{tikzpicture}

        \onslide<3>
        \begin{tikzpicture}[]
            \node [rum-node, fill=greenGood] (memory) at ( 3, 0) {Mem};
            \node [rum-node, fill=greenGood] (write) at (-3, 0) {Write};
            \node [rum-node, fill=redBad] (read) at ( 0, 3) {Read};
            \draw (read) -- (write) -- (memory) -- (read);
            \begin{scope}[on background layer]
                \fill [gray, opacity=0.2]
                    (read.center) --
                    (write.center) --
                    (memory.center) -- cycle;
            \end{scope}

@@

    \begin{overprint}[8cm]
        \onslide<1>
        \begin{tabular}{lll}
            & Johnson David & 04-02-2019 \\
            & Miller Kevin & 01-02-2019 \\
            & Miller Ned & 02-03-2019 \\
            & Miller Steven & 03-04-2019 \\
            & Smith Jack & 01-02-2019 \\
        \end{tabular}

        \onslide<2>
        \begin{tabular}{lll}
            & Johnson David & 04-02-2019 \\
            & Miller Kevin & 01-02-2019 \\
            & \tikzmark{middle}Miller Ned & 02-03-2019 \\
            & Miller Steven & 03-04-2019 \\
            & Smith Jack & 01-02-2019 \\
        \end{tabular}
        \begin{tikzpicture}[overlay, remember picture]
            \node[arrow-pointer, left=0.5cm of {pic cs:middle}, yshift=0.2cm] {};
        \end{tikzpicture}

        \onslide<3>
        \begin{tabular}{lll}
            & Johnson David & 04-02-2019 \\
            & Miller Kevin & 01-02-2019 \\
            & \tikzmark{middle}\colorbox{BurntOrange}{Miller N}ed & 02-03-2019 \\
            & Miller Steven & 03-04-2019 \\
            & Smith Jack & 01-02-2019 \\
        \end{tabular}
        \begin{tikzpicture}[overlay, remember picture]
            \node[arrow-pointer, left=0.5cm of {pic cs:middle}, yshift=0.2cm] {};
        \end{tikzpicture}

        \onslide<4>
        \begin{tabular}{lll}
            & \tikzmark{middle}\colorbox{BurntOrange}{J}ohnson David & 04-02-2019 \\
            & Miller Kevin & 01-02-2019 \\
            & Miller Ned & 02-03-2019 \\
            & Miller Steven & 03-04-2019 \\
            & Smith Jack & 01-02-2019 \\
        \end{tabular}
        \begin{tikzpicture}[overlay, remember picture]
            \node[arrow-pointer, left=0.5cm of {pic cs:middle}, yshift=0.2cm] {};
        \end{tikzpicture}

@@

    %\begin{center}
    %\textbf{Interpolation search}
    %\vspace{1cm}

    %\begin{overprint}[12cm]
        %\onslide<1>
        %\begin{center}
        %\begin{tikzpicture}[]
            %\node[draw] (key1) {5};
            %\foreach \i / \value [evaluate=\i as \prev using \i-1] in
                %{2/9,3/12,4/16,5/19,6/21,7/25,8/27,9/31,10/34,11/36}
            %{
                %\node[draw, right=0 of key\prev] (key\i) {\value};
            %}
        %\end{tikzpicture}
        %\end{center}

        %\onslide<2>
        %\begin{center}
        %\begin{tikzpicture}[]
            %\node[draw] (key1) {5};
            %\foreach \i / \value [evaluate=\i as \prev using \i-1] in
                %{2/9,3/12,4/16,5/19,6/21,7/25,8/27,9/31,10/34,11/36}
            %{
                %\node[draw, right=0 of key\prev] (key\i) {\value};
            %}

            %\coordinate[below=2cm of key1] (start);
            %\draw[->, btree-line] (start.south)
                %.. controls ([xshift=1cm] start) and ([yshift=-3cm] key6) ..
                %(key6.south);
            %\draw[->, btree-line] (key6.south)
                %.. controls ([yshift=-3cm] key6) and ([yshift=-3cm] key9) ..
                %(key9.south);
            %\draw[->, btree-line] (key9.south)
                %.. controls ([yshift=-2cm] key9) and ([yshift=-2cm] key10) ..
                %(key10.south);

        %\end{tikzpicture}
        %\end{center}

        %\onslide<3>
        %\begin{center}
        %\begin{tikzpicture}[xscale=0.6, yscale=0.1]
            %\draw[->] (0,0) -- (11,0);
            %\draw[->] (0,0) -- (0,36);
            %\draw[color=red, line width=2pt] plot[id=x] file {\strongdata};
        %\end{tikzpicture}
        %\end{center}

        %\onslide<4>
        %\begin{center}
        %\begin{tikzpicture}[]
            %\node[draw] (key1) {5};
            %\foreach \i / \value [evaluate=\i as \prev using \i-1] in
                %{2/9,3/12,4/16,5/19,6/21,7/25,8/27,9/31,10/34,11/36}
            %{
                %\node[draw, right=0 of key\prev] (key\i) {\value};
            %}

            %\coordinate[below=2cm of key6] (start);
            %\draw[->, btree-line] (start.south)
                %.. controls ([xshift=1cm] start) and ([yshift=-3cm] key10) ..
                %(key10.south);

        %\end{tikzpicture}
        %\end{center}

        %\onslide<5>
        %\begin{center}
        %\begin{tikzpicture}[]
            %\node[draw] (key1) {5};
            %\foreach \i / \value [evaluate=\i as \prev using \i-1] in
                %{2/6,3/15,4/15,5/16,6/43,7/95,8/96,9/97,10/128,11/499}
            %{
                %\node[draw, right=0 of key\prev] (key\i) {\value};
            %}

        %\end{tikzpicture}
        %\end{center}

        %\onslide<6>
        %\begin{center}
        %\begin{tikzpicture}[xscale=0.6, yscale=0.008]
            %\draw[->] (0,0) -- (11,0);
            %\draw[->] (0,0) -- (0,499);
            %\draw[color=red, line width=2pt] plot[id=x] file {\weakdata};
        %\end{tikzpicture}
        %\end{center}
    %\end{overprint}

    %\end{center}
%\end{frame}

@@

@@

    \begin{center}
    \textbf{Trie}
    \vspace{0.2cm}

    \begin{overprint}[12cm]
        \onslide<1>
        \begin{tikzpicture}[]
            \node[minimum width=12cm] (base) {};
            \node[trie-node] (node1) at (base.north) {};
            \trienode{1}{2}{0}{-1.75cm}{}
            \trienode{1}{3}{1}{1.75cm}{}

            \trienode{2}{4}{01}{-1.0cm}{}
            \trienode{2}{5}{1}{1.0cm}{}
            \trienode{3}{6}{0}{-1.0cm}{10}
            \trienode{3}{7}{11}{1.0cm}{}

            \trienode{4}{8}{0}{-0.5cm}{0010}
            \trienode{4}{9}{1}{0.5cm}{}
            \trienode{5}{10}{0}{-0.5cm}{010}
            \trienode{5}{11}{1}{0.5cm}{011}
            \trienode{7}{12}{0}{-0.5cm}{}
            \trienode{7}{13}{1}{0.5cm}{1111}

            \trienode{9}{14}{00}{-0.5cm}{}
            \trienode{9}{15}{00}{0.5cm}{001100}
            \trienode{12}{16}{01}{-0.5cm}{111001}
            \trienode{12}{17}{1}{0.5cm}{11101}

            \trienode{14}{18}{0}{-0.5cm}{0011000}
            \trienode{14}{19}{1}{0.5cm}{0011001}
        \end{tikzpicture}

        \onslide<2>
        \begin{tikzpicture}[]
            \node[minimum width=12cm] (base) {};
            \node[trie-node] (node1) at (base.north) {};
            \trienode{1}{2}{0}{-1.75cm}{}
            \trienode{1}{3}{1}{1.75cm}{}
            \node[draw, dashed, rounded corners, behind path, inner sep=0.2, fit=(node1)(node2)(node3)] {};

            \trienode{2}{4}{01}{-1.0cm}{}
            \trienode{2}{5}{1}{1.0cm}{}
            \trienode{3}{6}{0}{-1.0cm}{10}
            \trienode{3}{7}{11}{1.0cm}{}

            \trienode{4}{8}{0}{-0.5cm}{0010}
            \trienode{4}{9}{1}{0.5cm}{}
            \trienode{5}{10}{0}{-0.5cm}{010}
            \trienode{5}{11}{1}{0.5cm}{011}
            \trienode{7}{12}{0}{-0.5cm}{}
            \trienode{7}{13}{1}{0.5cm}{1111}
            \node[draw, dashed, rounded corners, behind path, inner sep=0.2, fit=(node4)(node5)(node8)(node9)(node10)(node11)] {};
            \node[draw, dashed, rounded corners, behind path, inner sep=0.2, fit=(node6)(node7)(node12)(node13)] {};

            \trienode{9}{14}{00}{-0.5cm}{}
            \trienode{9}{15}{00}{0.5cm}{001100}
            \trienode{12}{16}{01}{-0.5cm}{111001}
            \trienode{12}{17}{1}{0.5cm}{11101}
            \node[draw, dashed, rounded corners, inner sep=0.1, behind path, fit=(node16)(node17)] {};

            \trienode{14}{18}{0}{-0.5cm}{0011000}
            \trienode{14}{19}{1}{0.5cm}{0011001}

            \node[draw, dashed, rounded corners, behind path, inner sep=0.2, fit=(node14)(node15)(node18)(node19)] {};
        \end{tikzpicture}
        \linespread{0.5}
        \color{black}\fontsize{6pt}{0}\selectfont
            Leis V., Kemper Alfons, Neumann Thomas. (2013). The adaptive radix
            tree: ARTful indexing for main-memory databases. Proceedings -
            International Conference on Data Engineering. 38-49.
        \linespread{1.5}

        \onslide<3>
        \begin{tikzpicture}[]
            \node[minimum width=12cm] (base) {};
            \node[trie-node, fill=greenGood] (node1) at (base.north) {};
            \trienode{1}{2}{0}{-1.75cm, fill=greenGood}{}
            \trienode{1}{3}{1}{1.75cm, fill=greenGood}{}

            \coordinate[left=0.35cm of node2] (node2-shift);
            \node[trie-node, fill=blue!20, below=0.35cm of node2-shift] (node2-shift-target) {};
            \trienode{2-shift-target}{4}{01}{-1.0cm, fill=blue!20}{}
            \trienode{2-shift-target}{5}{1}{1.0cm, fill=blue!20}{}
            \draw[-, btree-line, dotted] (node2) -- (node2-shift-target);

            \coordinate[right=0.35cm of node3] (node3-shift);
            \node[trie-node, fill=yellow!20, below=0.35cm of node3-shift] (node3-shift-target) {};
            \trienode{3-shift-target}{6}{0}{-1.0cm, fill=yellow!20}{10}
            \trienode{3-shift-target}{7}{11}{1.0cm, fill=yellow!20}{}
            \draw[-, btree-line, dotted] (node3) -- (node3-shift-target);

            \trienode{4}{8}{0}{-0.5cm, fill=blue!20}{0010}
            \trienode{4}{9}{1}{0.5cm, fill=blue!20}{}

            \coordinate[right=0.35cm of node5] (node5-shift);
            \node[trie-node, fill=red!20, below=0.35cm of node5-shift] (node5-shift-target) {};
            \trienode{5-shift-target}{10}{0}{-0.5cm, fill=red!20}{010}
            \trienode{5-shift-target}{11}{1}{0.5cm, fill=red!20}{011}
            \draw[-, btree-line, dotted] (node5) -- (node5-shift-target);

            \coordinate[left=0.35cm of node7] (node7-shift);
            \node[trie-node, fill=gray!20, below=0.35cm of node7-shift] (node7-shift-target) {};
            \trienode{7-shift-target}{12}{0}{-0.5cm, fill=gray!20}{}
            \trienode{7-shift-target}{13}{1}{0.5cm, fill=gray!20}{1111}
            \draw[-, btree-line, dotted] (node7) -- (node7-shift-target);

            \coordinate[right=0.35cm of node9] (node9-shift);
            \node[trie-node, fill=Sepia!20, below=0.35cm of node9-shift] (node9-shift-target) {};
            \trienode{9-shift-target}{14}{00}{-0.5cm, fill=Sepia!20}{}
            \trienode{9-shift-target}{15}{00}{0.5cm, fill=Sepia!20}{001100}
            \trienode{14}{18}{0}{-0.5cm, fill=Sepia!20}{0011000}
            \trienode{14}{19}{1}{0.5cm, fill=Sepia!20}{0011001}
            \draw[-, btree-line, dotted] (node9) -- (node9-shift-target);

            \trienode{12}{16}{01}{-0.5cm, fill=gray!20}{111001}
            \trienode{12}{17}{1}{0.5cm, fill=gray!20}{11101}
        \end{tikzpicture}
        \linespread{0.5}
        \color{black}\fontsize{6pt}{0}\selectfont
            Binna Robert, Zangerle Eva, Pichl Martin, Specht Guenther, Leis
            Viktor. (2018). HOT: A Height Optimized Trie Index \\
            for Main-Memory Database Systems. 521-534.
        \linespread{1.5}

@@

    \end{center}
\end{frame}
\note{
    Silo - Masstree
    HyPer - ART
    ClickHouse - BTrie
}

>>>>

\usepackage[utf8]{inputenc}
\usepackage[russian, english]{babel}
\usepackage{booktabs}
\usepackage[scale=2]{ccicons}
\usepackage{listings}
\usepackage{marvosym}
\usepackage{color}
\usepackage{xcolor}
\usepackage[document]{ragged2e}
\usepackage[export]{adjustbox}
\usepackage{fontawesome5}
\usepackage{enumitem}
\usepackage{minted}
\usemintedstyle{tango}
\usepackage[normalem]{ulem}
\usepackage{tikz}
\usetikzlibrary{patterns}
\usetikzlibrary{mindmap}
\usetikzlibrary{shapes.misc, fit}
\usetikzlibrary{spy, decorations, decorations.pathmorphing, decorations.pathreplacing, backgrounds}
\usepackage{graphicx}
\usepackage{eso-pic}
\usepackage{verbatim}
\usepackage{smartdiagram}
\usesmartdiagramlibrary{additions}
\usetikzlibrary{trees}
\usepackage{datetime}
\usepackage{hyperref}
\usepackage{forloop}
\usepackage{csquotes}
\usetikzlibrary{tikzmark}
\usetikzlibrary{arrows.meta}

@@

\usetikzlibrary{shapes,arrows,positioning}
\graphicspath{{images/}}
%\newfontfamily{\FA}{FontAwesome}

\def\twitter{{\faTwitter}}
\def\github{{\faGithub}}
\def\email{{\faEnvelope}}

\renewcommand{\ttdefault}{pcr}
\setmonofont{FiraCode-VF}
%\newfontfamily{\ttfamily}{FiraCode-VF}

@@

\definecolor{links}{HTML}{0099FF}
\hypersetup{colorlinks, linkcolor=, urlcolor=links}
\definecolor{greenGood}{HTML}{99FF99}
\definecolor{redBad}{HTML}{FF9980}
\definecolor{title}{HTML}{ee0000}

@@

\setbeamertemplate{navigation symbols}{}
\beamertemplatenavigationsymbolsempty
\pagenumbering{gobble}

@@

  \vspace*{2.1cm}
  \hspace{7.0cm}
  \begin{minipage}[b][\paperheight]{0.5\textwidth}
  \begin{center}

    \ifx\inserttitle\@empty\else
    {{% \inserttitle is nonempty
      \raggedright%
      %\linespread{1.0}%
      \usebeamerfont{title}%
      \usebeamercolor[fg]{title}%
      %\vspace*{1.3em}
      \if@noSmallCapitals%
        \inserttitle%
      \else%
        \scshape{\color{title} \textbf{\begin{flushleft}\inserttitle\end{flushleft}}}%
      \fi%
      \vspace*{0.3em}
    }}
    \fi

@@

    \usebeamerfont{author}%
    \usebeamercolor[fg]{author}%
    {\begin{flushleft}\color{black} \insertauthor\end{flushleft}}%

    %\vspace*{1.5em}
    \fontsize{8pt}{10}\selectfont
    {\begin{flushleft}\color{black} 12-09-2022\end{flushleft}}%

@@

\title{Modern BTree techniques}
\subtitle{}
\date{\today}
\author{DMITRII DOLGOV}
\institute{}

@@

\begin{document}
{
  \usebackgroundtemplate{\includegraphics[width=\paperwidth]{title.png}}%
  \fontsize{17pt}{18}\selectfont
  \maketitle
}

\AddToShipoutPictureBG{
  \AtPagemyUpperLeft{{\includegraphics[width=2.0cm,keepaspectratio]{logo.png}}}
}

\setbeamertemplate{background canvas}{}

@@

\begin{frame}
    \frametitle{}
    \begin{center}
        \only<1>{
            \includegraphics[width=0.5\textwidth,center]{real-btree-resized.png}
        }
        \only<2>{
            \includegraphics[width=0.5\textwidth,center]{neato-btree.png}
        }
    \end{center}
\end{frame}

@@

@@

@@

    \begin{overprint}[8cm]
        \onslide<1>
        \begin{tabular}{lll}
            & Cohen Richard & 02-02-2019 \\
            & Johnson David & 04-02-2019 \\
            & Miller Kevin & 01-02-2019 \\
            & Miller Mary & 02-03-2019 \\
            & Miller Steven & 03-04-2019 \\
            & Smith Susan & 01-02-2019 \\
        \end{tabular}

        \onslide<2>
        \begin{tabular}{lll}
            & Cohen Richard & 02-02-2019 \\
            & Johnson David & 04-02-2019 \\
            & Miller Kevin & 01-02-2019 \\
            \hline
            & \colorbox{BurntOrange}{Miller M}ary & 02-03-2019 \\
            & Miller Steven & 03-04-2019 \\
            & Smith Susan & 01-02-2019 \\
        \end{tabular}

        \onslide<3>
        \begin{tabular}{lll}
            & Cohen Richard & 02-02-2019 \\
            \hline
            & \colorbox{BurntOrange}{J}ohnson David & 04-02-2019 \\
            & Miller Kevin & 01-02-2019 \\
            & Miller Mary & 02-03-2019 \\
            & Miller Steven & 03-04-2019 \\
            & Smith Susan & 01-02-2019 \\
        \end{tabular}

@@

        \onslide<2>
        \begin{tikzpicture}[]
            \node [rum-node, fill=redBad] (memory) at ( 3, 0) {Mem};
            \node [rum-node, fill=redBad] (write) at (-3, 0) {Write};
            \node [rum-node, fill=greenGood] (read) at ( 0, 3) {Read};
            \draw (read) -- (write) -- (memory) -- (read);
            \begin{scope}[on background layer]
                \fill [gray, opacity=0.2]
                    (read.center) --
                    (write.center) --
                    (memory.center) -- cycle;
            \end{scope}

@@

\pgfdeclarelayer{background layer}
\pgfsetlayers{background layer,main}

@@

    \begin{center}
    \textbf{Learned Index}

    \begin{overprint}[14cm]
        \onslide<1>
        \begin{tikzpicture}
            [line cap=round,line join=round,x=2cm,y=2cm,
             %using the 'spy' to magnify a part of the picture
             spy using outlines={circle,lens={scale=2.5}, size=8cm, connect spies},
             %using the decoration 'brace' (=a curly brace as path replacement)
             decoration={brace,amplitude=2pt}]
        %main layer
        %creating the grid
          \draw [color=lightgray,dash pattern=on 1pt off 1pt, xstep=1cm,ystep=1cm]
                                                         (-0.1,-0.1) grid (2.3,2.3);
        %creating the ticks and xy-axis nodes
          \draw[-latex,color=darkgray,thin] (-0.2,0) -- (2.4,0);
           \foreach \x in {,1,2}
           \draw[shift={(\x,0)},color=darkgray,thin] (0pt,1pt) -- (0pt,-1pt)
                                           node[below] {\footnotesize $\x$};
          \draw[-latex,color=darkgray] (0,-0.2) -- (0,2.6);
              \foreach \y in {,1,2}
              \draw[shift={(0,\y)},color=darkgray,thin] (1pt,0pt) -- (-1pt,0pt)
                                            node[left] {\footnotesize $\y$};
          \draw[color=black] (0pt,-8pt) node[left] {\footnotesize $0$};
        %some function
          \draw[smooth,samples=1000,domain=0.0:2.2]
           plot(\x,{0.1*(8*\x-32.4*\x^2+49.48*\x^3-20.11*\x^4+0.594*\x^5+0.30*\x^7)});
                                    %-3.99*\x^6+0.465713*\x^7-0.0217374*\x^8});
          \draw [blue] (0.0,0.0)--(0.2,0.07) node [midway, above right]{};
          \draw [blue] (0.2,0.07)--(0.68,0.18) node [midway, above right]{};
          \draw [blue] (0.68,0.18)--(1.5,1.4) node [midway, above right]{};
          \draw [blue] (1.5,1.4)--(2.0,1.8) node [midway, above right]{};
          \draw [blue] (2.0,1.8)--(2.12,2.0) node [midway, above right]{};

        %creating the curly braces with decorate

          \draw [darkgray,ultra thin] (0,0.07)-- (0.42,0.07);
          \draw [darkgray,ultra thin] (0,0.12)-- (0.42,0.12);
          \draw [color=red] (0.0,0.07) -- (0.0,0.12)
           node [midway,anchor=east,inner sep=2pt, outer sep=1pt]{\tiny$\Delta$};

        %using the 'spy' to magnify a piece of the picture
          \spy [gray, size=7.4cm] on (0.42,0.08)
                     in node [left] at (6.5,1);

          \begin{pgfonlayer}{background layer}
           \node at (1.5,-0.5)[black]{Key space};
           \node at (-0.5,1.5)[black, rotate=90]{Position in index};
          \end{pgfonlayer}
        \end{tikzpicture}

@@

    \end{center}
\end{frame}
\note{
    At a high level, indexes (and B+ trees over sorted attributes
    in particular) can be represented by a function that maps
    a key (e.g., a timestamp) to a storage location. Using this
    representation, FITing-Tree partitions the key space into
    a series of disjoint linear segments that approximate the
    true function, since it is (generally) not possible to fully
    model the underlying data distribution. At the core of this
    process is a tunable error threshold which represents the
    maximum distance that the predicted location of any key
    inside a segment is from its actual location. Instead of storing
    all values in the key space, FITing-Tree stores only (1) the
    starting key of each linear segment and (2) the slope of the
    linear function in order to compute a key’s approximate
    position using linear interpolation.

    FITing-Tree stores the boundaries and slope of
    each segment (instead of each individual key) in a B+ tree,
    reducing the overall memory footprint of the index.

    Case for learned index structures:
    Hybrid indexes: Starting from the entire dataset (line 3), it trains first
    the topnode model. Based on the prediction of this top-node model, it then
    picks the model from the next stage (lines 9 and 10) and adds all keys
    which fall into that model (line 10). Finally, in the case of hybrid
    indexes, the index is optimized by replacing NN models with B-Trees if
    absolute min-/max-error is above a predefined threshold.

    PLEX
    PLEX is a combination of CHT [2] and RS [7]. We build
    a spline on the underlying data, and then index the spline
    points in a CHT. The resulting index structure features fast
    build times, error-bounded lookups, and is easy to use as it
    has only one hyperparameter, the maximum error ϵ.
    RS employs a radix table for indexing its spline points.
    However, when the keys of the dataset cannot be easily in-
    dexed by a radix table, i.e., the longest common prefixes of
    their binary representation are large, RS can have a decrease
    in performance. PLEX addresses this issue by replacing the
    radix table with a radix tree, represented by CHT.
}

    %\begin{center}
    %\textbf{Trie}
    %\vspace{0.2cm}

    %\begin{overprint}[12cm]
        %\onslide<1>
        %\begin{tikzpicture}[]
            %\node[minimum width=12cm] (base) {};
            %\node[trie-node] (node1) at (base.north) {};
            %\trienode{1}{2}{0}{-1.75cm}{}
            %\trienode{1}{3}{1}{1.75cm}{}

            %\trienode{2}{4}{01}{-1.0cm}{}
            %\trienode{2}{5}{1}{1.0cm}{}
            %\trienode{3}{6}{0}{-1.0cm}{10}
            %\trienode{3}{7}{11}{1.0cm}{}

            %\trienode{4}{8}{0}{-0.5cm}{0010}
            %\trienode{4}{9}{1}{0.5cm}{}
            %\trienode{5}{10}{0}{-0.5cm}{010}
            %\trienode{5}{11}{1}{0.5cm}{011}
            %\trienode{7}{12}{0}{-0.5cm}{}
            %\trienode{7}{13}{1}{0.5cm}{1111}

            %\trienode{9}{14}{00}{-0.5cm}{}
            %\trienode{9}{15}{00}{0.5cm}{001100}
            %\trienode{12}{16}{01}{-0.5cm}{111001}
            %\trienode{12}{17}{1}{0.5cm}{11101}

            %\trienode{14}{18}{0}{-0.5cm}{0011000}
            %\trienode{14}{19}{1}{0.5cm}{0011001}
        %\end{tikzpicture}

        %\onslide<2>
        %\begin{tikzpicture}[]
            %\node[minimum width=12cm] (base) {};
            %\node[trie-node] (node1) at (base.north) {};
            %\trienode{1}{2}{0}{-1.75cm}{}
            %\trienode{1}{3}{1}{1.75cm}{}
            %\node[draw, dashed, rounded corners, behind path, inner sep=0.2, fit=(node1)(node2)(node3)] {};

            %\trienode{2}{4}{01}{-1.0cm}{}
            %\trienode{2}{5}{1}{1.0cm}{}
            %\trienode{3}{6}{0}{-1.0cm}{10}
            %\trienode{3}{7}{11}{1.0cm}{}

            %\trienode{4}{8}{0}{-0.5cm}{0010}
            %\trienode{4}{9}{1}{0.5cm}{}
            %\trienode{5}{10}{0}{-0.5cm}{010}
            %\trienode{5}{11}{1}{0.5cm}{011}
            %\trienode{7}{12}{0}{-0.5cm}{}
            %\trienode{7}{13}{1}{0.5cm}{1111}
            %\node[draw, dashed, rounded corners, behind path, inner sep=0.2, fit=(node4)(node5)(node8)(node9)(node10)(node11)] {};
            %\node[draw, dashed, rounded corners, behind path, inner sep=0.2, fit=(node6)(node7)(node12)(node13)] {};

            %\trienode{9}{14}{00}{-0.5cm}{}
            %\trienode{9}{15}{00}{0.5cm}{001100}
            %\trienode{12}{16}{01}{-0.5cm}{111001}
            %\trienode{12}{17}{1}{0.5cm}{11101}
            %\node[draw, dashed, rounded corners, inner sep=0.1, behind path, fit=(node16)(node17)] {};

            %\trienode{14}{18}{0}{-0.5cm}{0011000}
            %\trienode{14}{19}{1}{0.5cm}{0011001}

            %\node[draw, dashed, rounded corners, behind path, inner sep=0.2, fit=(node14)(node15)(node18)(node19)] {};
        %\end{tikzpicture}
        %\linespread{0.5}
        %\color{black}\fontsize{6pt}{0}\selectfont
            %Leis V., Kemper Alfons, Neumann Thomas. (2013). The adaptive radix
            %tree: ARTful indexing for main-memory databases. Proceedings -
            %International Conference on Data Engineering. 38-49.
        %\linespread{1.5}

        %\onslide<3>
        %\begin{tikzpicture}[]
            %\node[minimum width=12cm] (base) {};
            %\node[trie-node, fill=greenGood] (node1) at (base.north) {};
            %\trienode{1}{2}{0}{-1.75cm, fill=greenGood}{}
            %\trienode{1}{3}{1}{1.75cm, fill=greenGood}{}

            %\coordinate[left=0.35cm of node2] (node2-shift);
            %\node[trie-node, fill=blue!20, below=0.35cm of node2-shift] (node2-shift-target) {};
            %\trienode{2-shift-target}{4}{01}{-1.0cm, fill=blue!20}{}
            %\trienode{2-shift-target}{5}{1}{1.0cm, fill=blue!20}{}
            %\draw[-, btree-line, dotted] (node2) -- (node2-shift-target);

            %\coordinate[right=0.35cm of node3] (node3-shift);
            %\node[trie-node, fill=yellow!20, below=0.35cm of node3-shift] (node3-shift-target) {};
            %\trienode{3-shift-target}{6}{0}{-1.0cm, fill=yellow!20}{10}
            %\trienode{3-shift-target}{7}{11}{1.0cm, fill=yellow!20}{}
            %\draw[-, btree-line, dotted] (node3) -- (node3-shift-target);

            %\trienode{4}{8}{0}{-0.5cm, fill=blue!20}{0010}
            %\trienode{4}{9}{1}{0.5cm, fill=blue!20}{}

            %\coordinate[right=0.35cm of node5] (node5-shift);
            %\node[trie-node, fill=red!20, below=0.35cm of node5-shift] (node5-shift-target) {};
            %\trienode{5-shift-target}{10}{0}{-0.5cm, fill=red!20}{010}
            %\trienode{5-shift-target}{11}{1}{0.5cm, fill=red!20}{011}
            %\draw[-, btree-line, dotted] (node5) -- (node5-shift-target);

            %\coordinate[left=0.35cm of node7] (node7-shift);
            %\node[trie-node, fill=gray!20, below=0.35cm of node7-shift] (node7-shift-target) {};
            %\trienode{7-shift-target}{12}{0}{-0.5cm, fill=gray!20}{}
            %\trienode{7-shift-target}{13}{1}{0.5cm, fill=gray!20}{1111}
            %\draw[-, btree-line, dotted] (node7) -- (node7-shift-target);

            %\coordinate[right=0.35cm of node9] (node9-shift);
            %\node[trie-node, fill=Sepia!20, below=0.35cm of node9-shift] (node9-shift-target) {};
            %\trienode{9-shift-target}{14}{00}{-0.5cm, fill=Sepia!20}{}
            %\trienode{9-shift-target}{15}{00}{0.5cm, fill=Sepia!20}{001100}
            %\trienode{14}{18}{0}{-0.5cm, fill=Sepia!20}{0011000}
            %\trienode{14}{19}{1}{0.5cm, fill=Sepia!20}{0011001}
            %\draw[-, btree-line, dotted] (node9) -- (node9-shift-target);
